Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r run maaslin, results = 'hide'} 
maaslin.force.vars <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")

unlink("maaslin_core", recursive = TRUE)

prepare.maaslin(pseq.genus,
                 tsvfile = "maaslin_core_merged_phfinrisk_genus.tsv",
                conffile = "maaslin_core_config.config",
                includedvars = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION", maaslin.force.vars),
                core = TRUE,
                readpclrows = "Halapricum.Archaea-")

Maaslin("maaslin_core_merged_phfinrisk_genus.tsv",
        "maaslin_core",
        strInputConfig = "maaslin_core_config.config",
        strModelSelection="none",
        dSignificanceLevel = 1.0, 
        fAllvAll = TRUE,
        strForcedPredictors = maaslin.force.vars)
```

```{r lactobacillus scatterplot,  results = 'hide'}
pseq.lacto  <- subset_taxa(pseq.species, Genus=="Lactobacillus")
maaslin.force.vars.lacto <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")

unlink("maaslin_lacto", recursive = TRUE)

prepare.maaslin(pseq.lacto,
                 tsvfile = "maaslin_lacto_merged_phfinrisk_genus.tsv",
                conffile = "maaslin_lacto_config.config",
                includedvars = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION", maaslin.force.vars.lacto),
                readpclrows = "Lactobacillus_delbrueckii.Bacteria,Lactobacillus_ruminis.Bacteria,Lactobacillus_acidophilus.Bacteria,Lactobacillus_fermentum.Bacteria,Lactobacillus_paracasei.Bacteria,Lactobacillus_salivarius.Bacteria")

Maaslin("maaslin_lacto_merged_phfinrisk_genus.tsv",
        "maaslin_lacto",
        strInputConfig = "maaslin_lacto_config.config",
        strModelSelection="none",
        dSignificanceLevel = 1.0, 
        fAllvAll = TRUE,
        strForcedPredictors = maaslin.force.vars.lacto)
```

@@

```{r maaslin}
maas.results.df.signf <- read.table("maaslin_core/maaslin_core_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

```{r Reading maaslin lacto output}
maas.lacto.results.df.signf <- read.table("maaslin_lacto/maaslin_lacto_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%

>>>>

```{r maaslin runs, results = 'hide'} 
maaslin <- list()

maalin$genus <- maaslinwrapper(pseq = pseq.genus,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

lactotaxa <- paste0(c("Lactobacillus_delbrueckii.Bacteria", "Lactobacillus_ruminis.Bacteria", "Lactobacillus_acidophilus.Bacteria",
                    "Lactobacillus_fermentum.Bacteria", "Lactobacillus_paracasei.Bacteria", "Lactobacillus_salivarius.Bacteria"), collapse = ",")

maalin$lacto.min <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa = lactotaxa)

maalin$lacto.max  <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = lactotaxa)
```

@@

```{r maaslin}
maas.results.df.signf <- maaslin$genus %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

Lacto min

```{r Reading maaslin lacto min output}
maas.lacto.results.df.signf <- maaslin$lacto.min %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%

Lacto max

```{r Reading maaslin lacto max output}
maas.lacto.results.df.signf <- maaslin$lacto.max %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%
